---
title: "SEDA -- Census"
subtitle: "Data merge"
author:
- "Nathan Alexander, PhD"
- "Center for Applied Data Science and Analytics (CADSA)"
- "School of Education"
- "Howard University"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    theme: cerulean
    always_allow_html: true
    self_contained: true
  pdf: null
  pdf_document:
    toc: true
    toc_depth: '2'
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=T, message=F, warning=F}
knitr::opts_chunk$set(echo = TRUE)

pkgs <- c("tidycensus", "tidyverse", "mapview", "survey", "srvyr", "arcgislayers")
# install.packages(pkgs) # uncomment to install the packages

library(tidyverse)
library(tidycensus)
library(sf)
library(tidyverse)
library(ggplot2)
library(weights)
library(dplyr)
library(stringr)

options(tigris_use_cache = TRUE)

# data import
# install.packages("readstata13").
library(readstata13)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(weights)
library(here)
here::i_am("seda_census.Rmd")
```

# Census-CBSA

```{r, message=F, warning=F}
race_vars <- c(
  Hispanic = "P5_010N",
  White = "P5_003N",
  Black = "P5_004N",
  Native = "P5_005N",
  Asian = "P5_006N",
  HIPI = "P5_007N"
)

# Core-Based Statistical Areas (CBSA)
cbsa_race <- get_decennial(
  geography = "cbsa",
  variables = race_vars,
  summary_var = "P5_001N", 
  year = 2020,
  sumfile = "dhc"
)

glimpse(cbsa_race)
```

# SEDA-CBSA

SEDA Core-Based Statistical Area (2023 definition)

```{r}
cbsa23 <- read.dta13("../data/school_seg_cbsa23_1.0.dta")
glimpse(cbsa23)
```

## SEDA 2020 data

Filter for 2020 data.

```{r}
cbsa23 %>% 
  filter(year == 2020) -> cbsa_2020
glimpse(cbsa_2020)
```

# Merge

```{r}
merge <- left_join(cbsa_2020, cbsa_race, by = c("cbsa23id" = "GEOID"))
glimpse(merge)
```

# Analysis

## Variable descriptors

Variables represent cross-sectional (xs) racial achievement gaps, with "wht" referring to White students, "blk" to Black students, "hsp" to Hispanic students, "asn" to Asian students, "nam" to Native American students, "min" to minority students, and "nwh" to non-White Hispanic students. "was" refers to White achievement score. For example, `xs_wht_blk` represents the cross-sectional achievement gap between White and Black students.

## DC

```{r}
merge %>% 
  filter(cbsa23id == 47900) -> dc_census_seda

dc_census_seda %>% 
  relocate(variable, value) %>% 
  select(variable, value, cbsa23name, starts_with("sg_")) %>% 
  glimpse()
```


