---
title: "Stanford Education Data Archive (SEDA)"
subtitle: "Data Import"
author:
- "Nathan Alexander, PhD"
- "Center for Applied Data Science and Analytics (CADSA)"
- "School of Education"
- "Howard University"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    theme: cerulean
    always_allow_html: true
    self_contained: true
  pdf: null
  pdf_document:
    toc: true
    toc_depth: '2'
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=T, message=F, warning=F}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F, warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(weights)
library(here)
here::i_am("seda-import.Rmd")
```

We import and prepare for the analysis of the [Stanford Education Data Archive (SEDA) data](https://edopportunity.org/).

# DATA

## State data

```{r}
state_data <- data.frame(state.x77)
state_data$state <- tolower(rownames(state_data))

```


## Segregation Tracking Project (STP) data

The [STP data](https://edopportunity.org/segregation/) is described as "a comprehensive resource for tracking segregation in the U.S., across every neighborhood and every school."

# References

Reardon, Sean F., Ann Owens, Demetra Kalogrides, Heewon Jang, and Thalia Tom. 2024. The Segregation Explorer (Version 1.0). http://edopportunity.org/segregation
